Superphy: Real-time prediction of \textit{E. coli} phenotype using graph-based genome sequence storage and retrieval with the \textit{spfy} module

### 2017-11-02 paper-webserver.tex
START: on the beef

% 3. 100,000 genomes, (lookup number for Enterobase, GenBank), how do we run analysis on it
WGS data for bacterial pathogens of public health importance have recently accumulated in public databases in the tens of thousands, with hundreds of thousands set to be available within the next few years. For \textit{Escherichia coli}, there are over sixty thousand publicly available genomes in EnteroBase \url{https://enterobase.warwick.ac.uk/} and X whole genomes in GenBank \cite{doi:10.1093/nar/gks1195}.

@@

% 3. how we solved it
In this study, we present an update to the SuperPhy platform, called Spfy. The update rewrites the result storage by using a graph database, and takes a modular approach to tool integration, and distributes analyses over task queues; this allows users to submit genomes and modules to run in parallel in real-time.

>>>>

% 3. 100,000 genomes, (lookup number for Enterobase, GenBank), how do we run analysis on it
WGS data for bacterial pathogens of public health importance have recently accumulated in public databases in the tens of thousands, with hundreds of thousands set to be available within the next few years. For \textit{Escherichia coli}, there are over sixty thousand publicly available genomes in EnteroBase \url{https://enterobase.warwick.ac.uk/} and three million whole genomes in GenBank \cite{doi:10.1093/nar/gks1195}.

@@

% 3. how we solved it
In this study, we present an update to the SuperPhy platform, called Spfy. Spfy enables large-scale genome processing in real-time and uniquely decomposses results into graph datastructures for further comparative genomics. Unlike traditional approaches which store results in separate data files or in a relational database, our graph datastructures are then integrated into a knowledge graph identifying relationships between all genomes sequenced in the past, present, and future. We present the use of graph databases as a solution to storing genome analysis results in a meaningful manner, and to allow retrospective comparisons as more genomes are sequenced or populations change.

{I'm not sure if we should include that the same graph database can be expanded to cover different spcies}
